A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-10 final project/Manuscript.Rmd
Additional work on final project

df <- df %>%
  mutate(MOSTYPE = as.factor(MOSTYPE),
         MGEMLEEF = as.factor(MGEMLEEF),
         MOSHOOFD = as.factor(MOSHOOFD),
         MGODRK = as.factor(MGODRK),
         PWAPART = as.factor(PWAPART),
         CARAVAN = as.factor(CARAVAN)) %>%
  mutate(MOSTYPE = recode(MOSTYPE, !!!MOSTYPE_labels),
         MGEMLEEF = recode(MGEMLEEF, !!!MGEMLEEF_labels),
         MOSHOOFD = recode(MOSHOOFD, !!!MOSHOOFD_labels),
         MGODRK = recode(MGODRK, !!!MGODRK_labels),
         PWAPART = recode(PWAPART, !!!PWAPART_labels))
}

@@

```{r, echo=FALSE}
doornik <- function(df) {
  df <- df %>%
    mutate(PBRAND_2_or_6 = ifelse(PBRAND == 2 | PBRAND == 6, 1, 0),
           PBRAND_3_or_4 = ifelse(PBRAND == 3 | PBRAND == 4, 1, 0),
           PPLEZIER_gt_0 = ifelse(PPLEZIER > 0, 1, 0),
           PPERSAUT_6 = ifelse(PPERSAUT == 6, 1, 0))
  z <- -4.1 - (0.13 * df$MOPLLAAG) - (0.3 * df$MINK123M) + (0.17 * df$MINKGEM) + (0.54 * (df$ALEVEN + df$AFIETS + df$ABYSTAND)) - df$PBRAND_2_or_6 + (0.8 * df$PBRAND_3_or_4) + (2.4 * df$PPLEZIER_gt_0) + (1.5 * df$PPERSAUT_6) + (0.28 * (df$PWAOREG - df$PLEVEN))
  p_caravan <- exp(z) / (1 + exp(z))
  #p_caravan
  ifelse(p_caravan > 0.5, 1, 0)
}

eval$doornik <- doornik(eval)
```

>>>>

df %>%
  mutate(MOSTYPE = as.factor(MOSTYPE),
         MGEMLEEF = as.factor(MGEMLEEF),
         MOSHOOFD = as.factor(MOSHOOFD),
         MGODRK = as.factor(MGODRK),
         PWAPART = as.factor(PWAPART),
         CARAVAN = as.factor(CARAVAN)) %>%
  mutate(MOSTYPE = recode(MOSTYPE, !!!MOSTYPE_labels),
         MGEMLEEF = recode(MGEMLEEF, !!!MGEMLEEF_labels),
         MOSHOOFD = recode(MOSHOOFD, !!!MOSHOOFD_labels),
         MGODRK = recode(MGODRK, !!!MGODRK_labels),
         PWAPART = recode(PWAPART, !!!PWAPART_labels))
}

@@
